\chapter*{Acknowledgments}

This research was possible thanks to the support of several institutions.
The Secretary of Higher Education, Science, Technology and Innovation
of Ecuador (SENESCYT) provided funding for my PhD studies. The Ecuadorian
Institute of Meteorology and Hydrology (INAMHI) and Risk Frontiers
Research Centre contributed with climate data and bushfire records
respectively. Additionally, the Australian Research Council's (ARC)
Centre of Excellence for Climate System Science offered exciting professional
development opportunities during my candidature.

My most sincere thanks to my supervisors Professor David Karoly and
Dr Alexandre Pezza. Their insightful mentorship was crucial in the
most difficult times of my PhD journey. It was a privilege to work
with them. I also extend my appreciation to the other members of my
advisory panel, Associate Professor Kevin Walsh and Dr Roger Dargaville
for their constructive comments on my work. 

I wish to acknowledge the support received from the staff of the School
of Earth Sciences during my studies. In particular, to Dr John Moreau
and Professor Ian Simmonds for their help as coordinators of the PhD
program. I am grateful to Kevin Keay for his computing advice. To
my fellow PhD students Pilar Barria, Robert Huva, Mitchell Black,
Damien Irving, and Linden Ashcroft my deepest sentiment of gratitude
for sharing their expertise. I am proud to have met these talented
people. I also want to thank Ben Mather, Adam Beall and Jan Tympel
with whom I shared an office as well wonderful moments of my life
in Australia.

I am forever in debt to my parents, Milton Pazmi\~no and Yolanda Vernaza,
for all the sacrifices they made to help me achieve this goal. Finally,
I dedicate this work to my fiancée Natalia Rios. Her extraordinary
capacity to love gave me the strength to complete this dissertation. 
